Twists of supersymmetric gauge theories

### 2020-01-08 paper.tex
Minor changes

Given a vector bundle $E\rightarrow M$ we denote by $\cE$ the topological vector space of smooth sections of $E$ and $\cE_c$ the topological vector space of smooth compactly supported sections.
We denote by $\cO(\cE)$ (respectively $\cO(\cE_c)$) the completed algebra of functions on $\cE$ (respectively $\cE_c)$. 
For conventions on functions on topological vector spaces we refer to Appendix \ref{appx: top}. 
We denote by $\oloc(\cE)$ the space of local functionals on $\cE$ (see \cite[Definition 4.5.1.1]{Book2}). An element of $\oloc(\cE)$ will be denoted by
\[\int_M f (\phi, \phi', \dots),\]
where $f$ is a density on $M$ depending on infinite jets of sections of $E$. Note, however, that the integral here is a formal symbol. 
The space of local functionals can be viewed as a subspace
\[
\oloc(\cE) \subset \cO(\cE_c)
\]
where we the integral symbol makes sense in earnest on sections which are compactly supported.
We denote by $\oloc^+(\cE)\subset \oloc(\cE)$ the subspace of local functionals which are at least cubic.

@@

\item A ghost field $c\in\Gamma(V_\RR; \Pi\fg)$.
\end{itemize}
We also introduce their antifields $A^*\in\Omega^1(V_\RR; \Pi\fg)$, $\lambda\in\Gamma(V_\RR; \Sigma^*\otimes \fg)$ and $c^*\in\Gamma(V_\RR; \fg)$.
Let $\cE_{\rm SYM}$ denote the space of BV fields.

@@

\begin{thm}\label{thm:gaugemultipletSUSY}
The functional $\fS_{\gauge} = S_{\gauge} + I_{\gauge}^{(1)} + I_{\gauge}^{(2)} \in C^\bu(\mf{A}, \oloc(\cE_{\rm SYM}))$ satisfies the classical master equation
\[\d_{CE} \fS_{\gauge} + \frac{1}{2}\{\fS_{\gauge}, \fS_{\gauge}\} = 0.\]
Thus, $\fS_{\gauge}$ defines an elliptic $L_\infty$ action of the super Lie algebra $\fA$ on super Yang-Mills theory and so super Yang-Mills theory is supersymmetric.  
\end{thm}

@@

\begin{thm}
The holomorphic twist of 9d $\mc N=1$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory on $\CC^4\times \RR$ with the space of fields $\map(\CC^4\times \RR_{\mr{dR}}, B\gg)$.
\end{thm}
\begin{proof}
By definition 9d $\mc N=1$ super Yang--Mills is obtained by a dimensional reduction of 10d $\mc N=(1, 0)$ super Yang--Mills along the projection $\RR^{10}\rightarrow \RR^9$. In complex coordinates, it is a dimensional reduction along the projection $\CC^4\times \CC\rightarrow \CC^4\times \RR$.

@@

@@

@@

\begin{theorem} \label{5d_rk4_twist_thm}
The twist by a rank $4$ supercharge of 5d $\mc N=2$ super Yang-Mills theory on an oriented 5-manifold $M_5$ is equivalent to 5d Chern-Simons theory on $M_5$: the $\ZZ/2\ZZ$-graded theory with space of fields $\mr{Map}(M_5, B\gg)$.
\end{theorem}

@@

% \cN=4 SYM
% \cN=2 SYM with matter in a pseudo-real representation
% \cN=1 SYM with matter in a complex representation

@@

\subsection{$\cN=2$ SYM with hypermultiplet matter}
%quaternionic is hyperkahler
%pseudo-real is quaternionic

\subsection{$\cN=4$ SYM}

@@

% \cN=8 SYM
% \cN=4 SYM with matter in a pseudo-real representation
% \cN=2 SYM with matter in a complex representation

@@

% \cN=(8, 8) SYM
% \cN=(4, 4) SYM with matter in a pseudo-real representation
% \cN=(2, 2) SYM with matter in a complex representation
%BRIAN FIND REFERENCE OF BELOW
% \cN=(0,2) SYM with matter 
% \cN=(0,4) SYM with matter
% \cN=(0,8) SYM with matter

>>>>

Given a vector bundle $E\rightarrow M$ we denote by $\cE$ the topological vector space of smooth sections of $E$ and $\cE_c$ the topological vector space of smooth compactly supported sections.
We denote by $\cO(\cE)$ (respectively $\cO(\cE_c)$) the completed algebra of functions on $\cE$ (respectively $\cE_c)$. 
We denote by $\oloc(\cE)$ the space of local functionals on $\cE$ (see \cite[Definition 4.5.1.1]{Book2}). An element of $\oloc(\cE)$ will be denoted by
\[\int_M f (\phi, \phi', \dots),\]
where $f$ is a density on $M$ depending on infinite jets of sections of $E$. Note, however, that the integral here is a formal symbol. 
The space of local functionals can be viewed as a subspace
\[
\oloc(\cE) \subset \cO(\cE_c)
\]
where we the integral symbol makes sense in earnest on sections which are compactly supported.
We denote by $\oloc^+(\cE)\subset \oloc(\cE)$ the subspace of local functionals which are at least cubic.

@@

\item A ghost field $c\in\Gamma(V_\RR; \Pi\fg)$.
\end{itemize}
We also introduce their antifields $A^*\in\Omega^1(V_\RR; \Pi\fg)$, $\lambda\in\Gamma(V_\RR; \Sigma^*\otimes \fg)$ and $c^*\in\Gamma(V_\RR; \fg)$.
Let $\cE_{\rm Super Yang-Mills}$ denote the space of BV fields.

@@

\begin{thm}\label{thm:gaugemultipletSUSY}
The functional $\fS_{\gauge} = S_{\gauge} + I_{\gauge}^{(1)} + I_{\gauge}^{(2)} \in C^\bu(\mf{A}, \oloc(\cE_{\rm Super Yang-Mills}))$ satisfies the classical master equation
\[\d_{CE} \fS_{\gauge} + \frac{1}{2}\{\fS_{\gauge}, \fS_{\gauge}\} = 0.\]
Thus, $\fS_{\gauge}$ defines an elliptic $L_\infty$ action of the super Lie algebra $\fA$ on super Yang-Mills theory and so super Yang-Mills theory is supersymmetric.  
\end{thm}

@@

\begin{thm}
\label{9d_twist_thm}
The holomorphic twist of 9d $\mc N=1$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory on $\CC^4\times \RR$ with the space of fields $\map(\CC^4\times \RR_{\mr{dR}}, B\gg)$.
\end{thm}
\begin{proof}
By definition 9d $\mc N=1$ super Yang--Mills is obtained by a dimensional reduction of 10d $\mc N=(1, 0)$ super Yang--Mills along the projection $\RR^{10}\rightarrow \RR^9$. In complex coordinates, it is a dimensional reduction along the projection $\CC^4\times \CC\rightarrow \CC^4\times \RR$.

@@

\begin{proof}
This follows by dimensional reduction of the 8d holomorphic twist of Theorem \ref{8d_holo_twist_thm} and its one-parameter degeneration along one of the directions which is not invariant in the holomorphic theory.  That is, by applying Proposition \ref{CS_to_BF_diml_red_prop} to the family $\map(X_4, B\gg)_{\mr{Hod}}$.
\end{proof}

@@

\begin{proof}
Again, this follows by dimensional reduction from 8 dimensions, this time from the intermediate twist of Theorem \ref{8d_rank2_twist_thm}, again by an application of Proposition \ref{CS_to_BF_diml_red_prop}.
\end{proof}

@@

\begin{theorem} \label{5d_rk4_twist_thm}
The twist by a rank $4$ supercharge of 5d $\mc N=2$ super Yang-Mills theory on an oriented 5-manifold $M_5$ is equivalent to 5d Chern-Simons theory on $M_5$: the $\ZZ/2\ZZ$-graded theory with space of fields $\mr{Map}((M_5)_{\mr{dR}}, B\gg)$.
\end{theorem}

@@

@@

\subsection{$\cN=2$ Super Yang-Mills with hypermultiplet matter}
%quaternionic is hyperkahler
%pseudo-real is quaternionic

\subsection{$\cN=4$ Super Yang-Mills}

@@

% \cN=8 Super Yang-Mills
% \cN=4 Super Yang-Mills with matter in a pseudo-real representation
% \cN=2 Super Yang-Mills with matter in a complex representation

@@

% \cN=(8, 8) Super Yang-Mills
% \cN=(4, 4) Super Yang-Mills with matter in a pseudo-real representation
% \cN=(2, 2) Super Yang-Mills with matter in a complex representation
%BRIAN FIND REFERENCE OF BELOW
% \cN=(0,2) Super Yang-Mills with matter 
% \cN=(0,4) Super Yang-Mills with matter
% \cN=(0,8) Super Yang-Mills with matter
